Spike-and-Slab Generalized Additive Models and Scalable Algorithms for High-Dimensional Data

### 2022-03-22 Manuscript/02-Method.Rmd
Correct typo

\bg{The proposed two-part SSL prior, particularly the group SSL prior of the nonlinear space coefficients, differs from previous group SSL priors \cite{Tang2018, Tang2019}, as the proposed prior follows the effect hierarchy principle. Effect hierarchy refers to the principle that "lower-order effects are more likely to be active than higher-order effects" defined by Chipman\cite{chipman2006prior}. To implement, we consider the shared latent indicator of nonlinear coefficients $\gamma^\tp_j$} depends on the value of the linear space latent indicator $\gamma_j$, while both latent indicators $\gamma_j and \gamma^\tp_j$ follow a Bernoulli distribution. While the probability of including the linear effect is $\theta_j$, the probability of including the nonlinear effect is $\bg{\gamma_{j}}\theta_j$.
$$
\begin{aligned}
&\gamma_{j} | \theta_j \sim Bin(1, \theta_j) & & 
&\gamma_{j}^\tp | \bg{\gamma_{j}, } \theta_j \sim Bin(1, \bg{\gamma_{j}}\theta_j).
\end{aligned}
$$
\bg{This is, when the linear effect is not selected, the probability of including the nonlinear effect drops from $\theta_j$ to 0. For the computational convenience, we analytically integrate $\theta_j$ out such that $\gamma_{j}^\tp | \theta_j \sim Bin(1, \theta_j^2)$.
}

>>>>

\bg{The proposed two-part SSL prior, particularly the group SSL prior of the nonlinear space coefficients, differs from previous group SSL priors \cite{Tang2018, Tang2019}, as the proposed prior follows the effect hierarchy principle. Effect hierarchy refers to the principle that "lower-order effects are more likely to be active than higher-order effects" defined by Chipman\cite{chipman2006prior}. To implement, we consider the shared latent indicator of nonlinear coefficients $\gamma^\tp_j$} depends on the value of the linear space latent indicator $\gamma_j$, while both latent indicators $\gamma_j and \gamma^\tp_j$ follow a Bernoulli distribution. While the probability of including the linear effect is $\theta_j$, the probability of including the nonlinear effect is $\bg{\gamma_{j}}\theta_j$.
$$
\begin{aligned}
&\gamma_{j} | \theta_j \sim Bin(1, \theta_j) & & 
&\gamma_{j}^\tp | \bg{\gamma_{j}, } \theta_j \sim Bin(1, \bg{\gamma_{j}}\theta_j).
\end{aligned}
$$
\bg{This is, when the linear effect is not selected, the probability of including the nonlinear effect drops from $\theta_j$ to 0. For the computational convenience, we analytically integrate $\gamma_j$ out such that $\gamma_{j}^\tp | \theta_j \sim Bin(1, \theta_j^2)$ (see the derivation in the Supporting Information).
}
